---
title: "Math Final Project"
author: "Joseph Elikishvili"
date: "August 12, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(hflights)
```

##### Arrival Delay will be represented by Random Variable X 
##### Departure Delay will be represented Random Variable Y

#### 1. First we look at the skew of both ArrDelay and DepDelay 

The Following Histogram is showing the distribution of Arrival Delays having positive skew
```{r}
library(ggplot2)
ggplot(hflights, aes(ArrDelay)) + geom_histogram() + xlim(-50, 250)
```


The Following Histogram is showing the distribution of Departure Delays also having positive skew
```{r}
ggplot(hflights, aes(DepDelay)) + geom_histogram() + xlim(-50, 250)
```

#### 2. Subsetting hflights and removing NA values from dataframe
```{r}
h=subset(hflights,select=c(ArrDelay,DepDelay))
h1=na.omit(h)

x= h1$ArrDelay
y= h1$DepDelay

length(x)
length(y)

quantile(x)
quantile(y)
```
Based on data above, We will be using 11 for 3rd Quartile of x and 0 for 2nd quartile of y

Next we are Calculating Values for x/y table

1.  X<=11,y<=0
```{r}
p1=nrow(subset(h1, ArrDelay <= 11 & DepDelay <= 0))
p1
```

2. X<=11, y>0
```{r}
p2=nrow(subset(h1, ArrDelay <= 11 & DepDelay > 0))
p2
```

3. X>11, Y<=0
```{r}
p3=nrow(subset(h1, ArrDelay > 11 & DepDelay <= 0))
p3
```

4. X>11, Y>0
```{r}
p4=nrow(subset(h1, ArrDelay > 11 & DepDelay > 0))
p4
```

Table of counts
```{r}
table = matrix(c(p1,p3,p1+p3,p2,p4,p2+p4,p1+p2,p3+p4,p1+p2+p3+p4), nrow=3, ncol=3)
colnames(table) = c("<=Q2",">Q2","Total")
rownames(table) = c("<=Q3",">Q3","Total")
table
```

Calculating a. P(X>x | Y>y)   
```{r}
a=(48548/223874)/.5
a
```

Calculating b.P(X>x, Y>y)  
```{r}
b=(54707/223874)*(109574/223874)
b
```

Calculating P (X <x | Y<y)
```{r}
c =(61026/223874)/.5
c
```

P(A|B)=P(A)P(B)? 
```{r}
A = 54707/223874
B = 109574/223874
```

Calculate P(A|B)
```{r}
(48548/223874)/.5
```

Calculate P(a)*P(B)
```{r}
A*B
```

Based on above calculations we can conclude that P(A|B) != P(A)P(B)

```{r}
t1=c(x,y)
t2=table(t1)
chisq.test(t2)
```

Based on above Chi-squared test we see that p<0.05, therefore we reject the Hypotheses that Arrival Delay and Departure Delay are independent.

#### 2. Descriptive and Inferential Statistics.

Below is a Scatter Plot of Arrival Delay and Departure Delay 
```{r}
library(plotly)
plot_ly(data = h1, x = ArrDelay, y =DepDelay, mode = "markers")
```
Scatter Plot sugest a strong correation between the delays times.

Next we calculate the 95% Confedence interval for the difference of the means
```{r}
t.test(x,y)
```

Derive a correlation matrix for two of the quantitative variables
```{r}
h=subset(hflights,select=c(ArrDelay,DepDelay))
h1=na.omit(h)
cor(h1$ArrDelay, h1$DepDelay)
corm = matrix(c(1,0.929,0.929,1),nrow=2,ncol=2)
corm
```

Test the hypothesis that the correlation between these variables is 0 and provide a 99% confidence interval
```{r}
cor.test(h1$ArrDelay, h1$DepDelay, conf.level = 0.99)
```
Based on above we reject the null hypothesis that the correleation between the variables is 0.


#### 3. Linear Algebra and Corelation
```{r}
precm = solve(corm)
precm
precm%*%corm
corm%*%precm
```
We are multipling precision matrix by correlation matrix and correlation matrix by precision matrix. As we can see we are getting an Identity Matrix as a result of both multipications. This is to be expected, although normally we get different awnser depending on the order of how we multiply 2 matricies, in this case the matricies are inverses of each outher, so we end up with a 2x2 Identity matrix as a result.

#### 4. Calculus-Based Probability & Statistics
```{r}
summary(h1$ArrDelay)
summary(h1$DepDelay)
```

We can see that minimum values are -70 and -33, so we will shift 71 to make sure minimal value is above 0.
```{r}
x=h1$ArrDelay+71
summary(x)
```

Histogram of Shifted Data
```{r}
plot_ly(x=x, type="histogram")
```

Histogram of Original Data
```{r}
plot_ly(x=hflights$ArrDelay, type="histogram")
```

Next Loading Masspackage and fitting to exponential function
```{r}
require(MASS)
l=fitdistr(x, "exponential")
l
l$estimate
samples=rexp(1000, l$estimate )
```

Below are 5th and 95th percentiles using the cumulative distribution function (CDF)
```{r}
quantile(samples, probs=0.95)
quantile(samples, probs=0.05)
```

Calculating 95% confidence interval from the empirical data, assuming normality. ( Using z=1.96 (.975) since we are dealing with 2 tails)
```{r}
mean(x)-1.96*sd(x)
mean(x)+1.96*sd(x)
```
Based on above calculations based on 95% Confidece Interval = 17.90564 < M < 138.283

```{r}
quantile(h1$ArrDelay, probs=0.95)
quantile(h1$ArrDelay, probs=0.05)
```
Above are 5th percentile and 95th percentile of the data
