---
<<<<<<< Updated upstream
title: "Project 3: Data Science Skills"
author: "Aaron Grzasko, Ahsanul Choudhury, Andrew Carson, Bruce Hao, Daniel Thonn, Dhananjay Kumar, Joseph Elikishvili"
date: "October 23, 2016"
output: 
  html_document:
    highlight: tango
    theme: united
    pdf_document: default
=======
title: "Project 3"
author: "Andrew Carson"
date: "October 16, 2016"
output: html_document
>>>>>>> Stashed changes
---

### Load Data

<<<<<<< Updated upstream
Now we load the data from the MySQL database.  First, a connection is created, then a query is formed.  The query is fetched and the results are returned.

```{r eval=TRUE, message=FALSE}
library(dbConnect)


#set variables for connecting to MySQL
=======
```{r eval=TRUE}
library(dbConnect)



>>>>>>> Stashed changes
username = 'data607'

password = 'project3'

dbname = 'ds_skills'

host = 'data607-project3.ce2dfe0qxt5q.us-west-2.rds.amazonaws.com'

myDb = dbConnect(MySQL(), user=username, password=password, dbname=dbname, host=host)


<<<<<<< Updated upstream
#write query string to pull data from tables in MySQL
=======

>>>>>>> Stashed changes
qryString = 'SELECT jobs.post_id, role_desc, city, state, keyword_desc 

FROM jobs

INNER JOIN locations

ON jobs.loc_id = locations.loc_id

INNER JOIN roles

ON jobs.role_id = roles.role_id

INNER JOIN post_keys

ON jobs.post_id = post_keys.post_id 

INNER JOIN  keywords

ON post_keys.key_id = keywords.key_id

;'


<<<<<<< Updated upstream
#pull query
selectQry = dbSendQuery(myDb, qryString)
results = fetch(selectQry, n = -1)

#display first 10 rows
head(results, n=10)
```
* * *

### Analysis
Our task is to answer the question: "Which are the most valued data science skills?"  The easiest way to answer this is to look at the most frequent keywords in our dataset.

```{r, message=FALSE}
=======

selectQry = dbSendQuery(myDb, qryString)

results = fetch(selectQry, n = -1)

##results
```
* * *

### Begin Analysis

```{r}
>>>>>>> Stashed changes
library(ggplot2)
library(tidyr)
library(dplyr)
library(knitr)
<<<<<<< Updated upstream
library(DT)
library(stringr)
=======
>>>>>>> Stashed changes

#trim white space
results$keyword_desc<-str_trim(results$keyword_desc)

# counts of keywords
keyword_counts<-data.frame(table(results$keyword_desc))
names(keyword_counts)<-c("Keyword","Freq")
<<<<<<< HEAD
head(arrange(keyword_counts,desc(Freq)), n=10)
<<<<<<< Updated upstream
=======
keyword_counts$Keyword<-as.character(keyword_counts$Keyword)
head(arrange(keyword_counts,desc(Freq)), n=11)
>>>>>>> 2c1a1277cf1b70add4891337b348c6db1efa15b2
```

We see that communication tops the list, followed by Excel, JAVA, SQL, machine learning, and Python.  R comes in at number 11.

We add a plot to visualize the result.
```{r, message=FALSE}
#plot of keyword counts
qplot(data = keyword_counts, x = reorder(Keyword, -Freq), y=Freq, xlab="Keyword", ylab="Frequency", main = "Keywords by Frequency", size=I(5)) +
      theme(text = element_text(),
        axis.text.x = element_text(angle=90, vjust=1)) 
```

Overall, we see programming languages (JAVA, Python), statistical languages (R, SAS), big data languages(Pig, Hive), big data technologies (mapreduce, Hadoop), standard data skills (Excel, SQL), and visualization (Tableau, d3).  We also see a lot of "soft skills" or broad topic knowledge like communication, deep learning, math, "big data", "data mining", etc.

Adding nuance, what sorts of roles are we looking at that matched our search query when finding data?

```{r, message=FALSE}
=======



>>>>>>> Stashed changes
#count of role description
distinct_roles<-distinct(select(results, post_id,role_desc))
distinct_roles<-data.frame(table(distinct_roles$role_desc))
names(distinct_roles)<-c("Role","Freq")
head(arrange(distinct_roles,desc(Freq)), n=10)

<<<<<<< Updated upstream
#plot of role description
qplot(data = subset(distinct_roles, Freq>3), x = reorder(Role, -Freq), y=Freq, xlab="Role", ylab="Frequency", main = "Role by Frequency", size=I(5)) +
      theme(text = element_text(),
        axis.text.x = element_text(angle=90, vjust=1)) 
```

The most frequent is "data-scientist", which makes sense since this is what we were looking for.  We can also see "machine-learning", "software-engineer", and "statistician" in the list.  Most role descriptions are unique, but could be further grouped if desired.

How do roles and skills align?  Take a look at the below table, and sort on the keyword to find which job titles use this skill the most:

```{r, message=FALSE}
=======
>>>>>>> Stashed changes
#role vs. keyword counts
role_vs_Keyword<-results %>%
  select(role_desc,keyword_desc) %>%
  group_by(role_desc, keyword_desc) %>%
  count(role_desc, keyword_desc) %>%
  spread(role_desc,n)
  
<<<<<<< Updated upstream

#keyword vs. role
keyword_vs_role<-results %>%
  select(role_desc,keyword_desc) %>%
  group_by(role_desc, keyword_desc) %>%
  count(role_desc, keyword_desc) %>%
  spread(keyword_desc,n)

#which roles require which skills?
datatable(keyword_vs_role)
```

Since we are most interested in "data scientists", let's look at job titles that match "data-scientist":

```{r, message=FALSE, warning=FALSE}
# show top keywords for data-scientist
top_data_scientist<-
  arrange(role_vs_Keyword, desc(`data-scientist`)) %>%
  select(keyword_desc, `data-scientist`) 

#plot data-scientist
qplot(data = top_data_scientist, x = reorder(keyword_desc, -`data-scientist`), y=`data-scientist`, xlab="Keyword", ylab="Frequency", main = "Data Scientist: Keyword by Frequency", size=I(5)) +
      theme(text = element_text(),
        axis.text.x = element_text(angle=90, vjust=1)) 
```

Machine learning, Excel, Python, statistics, Hadoop, R, and communication are the top skills.

What about anything that matches the pattern "data-scien"?  This will include all levels of data scientists and other job titles that have this pattern in it.

```{r, message=FALSE}
# show top keywords for anything like data scientist
top_data_scientist_all<-
  results %>%
  subset(str_detect(role_desc,"data-scien")) %>%
  select(keyword_desc) %>%
  group_by(keyword_desc) %>%
  count(keyword_desc) %>%
  arrange(desc(n))

#plot data-scientist: all
qplot(data = top_data_scientist_all, x = reorder(keyword_desc, -n), y=n, xlab="Keyword", ylab="Frequency", main = "All 'Data Scientists': Keyword by Frequency", size=I(5)) +
      theme(text = element_text(),
        axis.text.x = element_text(angle=90, vjust=1))   
```

We have machine learning, Python, Statistics, Math, SQL, data mining, communication, and R. 

Where are these jobs being offered?  We collected the city and state information with these job postings:
```{r}
=======
kable(role_vs_Keyword)

## show top keywords for each role
# Data Analyst
arrange(role_vs_Keyword, desc(`Data Analyst`)) %>%
  select(keyword_desc, `Data Analyst`) %>%
  slice(1:10)

# Data Engineer
arrange(role_vs_Keyword, desc(`Data Engineer`)) %>%
  select(keyword_desc, `Data Engineer`) %>%
  slice(1:10)

# Data_Scientist
arrange(role_vs_Keyword, desc(`Data_Scientist`)) %>%
  select(keyword_desc, `Data_Scientist`) %>%
  slice(1:10)

# Jr. Data Scientist
arrange(role_vs_Keyword, desc(`Jr. Data Scientist`)) %>%
  select(keyword_desc, `Jr. Data Scientist`) %>%
  slice(1:10)

# Sr. Data Scientist
arrange(role_vs_Keyword, desc(`Sr. Data Scientist`)) %>%
  select(keyword_desc, `Sr. Data Scientist`) %>%
  slice(1:10)



>>>>>>> Stashed changes
#count of city
distinct_city<-distinct(select(results, post_id, city))
distinct_city<-data.frame(table(distinct_city$city))
names(distinct_city)<-c("city","Freq")
head(arrange(distinct_city,desc(Freq)), n=10)
<<<<<<< Updated upstream
```

Seattle is the top city at 69, followed by Chicago at 10, and Plano at 9.

What is your city's favorite data science skill?

```{r}
=======

>>>>>>> Stashed changes
#city vs. keyword counts
city_vs_Keyword<-results %>%
  select(city,keyword_desc) %>%
  group_by(city, keyword_desc) %>%
  count(city, keyword_desc) %>%
  spread(city,n)
  
<<<<<<< Updated upstream
#keyword vs. city counts
keyword_vs_city<-results %>%
  select(city,keyword_desc) %>%
  group_by(city, keyword_desc) %>%
  count(city, keyword_desc) %>%
  spread(keyword_desc,n)

datatable(keyword_vs_city)
```

Finally, we have the state.  Washington, California, and Texas have the most job postings.  Which skills does your state prefer?
```{r}
=======
kable(city_vs_Keyword)



>>>>>>> Stashed changes
#count of state
distinct_state<-distinct(select(results, post_id, state))
distinct_state<-data.frame(table(distinct_state$state))
names(distinct_state)<-c("state","Freq")
head(arrange(distinct_state,desc(Freq)), n=10)


#state vs. keyword counts
state_vs_Keyword<-results %>%
  select(state,keyword_desc) %>%
  group_by(state, keyword_desc) %>%
  count(state, keyword_desc) %>%
  spread(state,n)
  
<<<<<<< Updated upstream
#keyword vs. state counts
keyword_vs_state<-results %>%
  select(state,keyword_desc) %>%
  group_by(state, keyword_desc) %>%
  count(state, keyword_desc) %>%
  spread(keyword_desc,n)

datatable(keyword_vs_state)
```

### Conclusion
<<<<<<< HEAD
Our team found that many skills we expected to be popular were: Python, Excel, big data technologies, SQL.  The most surprising result is that R is not as popular as we thought it would be or should be.  This may be due to the difficulty of extracting "R" from the text of a job description, as we would expect it to be on par with Python in popularity.  This would be something that we would investigate for further analysis.
=======
kable(state_vs_Keyword)


```
>>>>>>> Stashed changes

=======
Our team found that many skills we expected to be popular were: Python, Excel, big data technologies, machine learning, SQL.  Perhaps most surprising is that "communication" is the top skill. Clearly, "soft skills" are still very important even for more technically oriented data scientists.
>>>>>>> 2c1a1277cf1b70add4891337b348c6db1efa15b2

Another surprising result was that R is not as popular as we thought it would be.  This may be due to the difficulty of extracting "R" from the text of a job description, as we would expect it to be on par with Python in popularity.  We did some work on getting better extraction of "R", and while its numbers did improve, it still lags behind Python by quite a bit.