---
title: "624HW3"
author: "Joseph Elikishvili"
date: "September 16, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fpp)
```

# 624 HW3 HA6  Ex 6.2

### a.	 Plot the time series of sales of product A. Can you identify seasonal fluctuations and/or a trend?

```{r}
plot(plastics)
```

There appears to be an upward trend and seasonal fluctuations are clearly visible on the chart.


### b.	Use a classical multiplicative decomposition to calculate the trend-cycle and seasonal indices.

```{r}
fit <- decompose(plastics, type="multiplicative")
plot(fit)

```

### c.	Do the results support the graphical interpretation from part (a)?
Yes they do.  There is an uptrend present and seasonality is also present just like we observed in part A.


### d. Compute and plot the seasonally adjusted data.
```{r}
season = seasadj(fit)
plot(season)
```


### E. Change one observation to be an outlier (e.g., add 500 to one observation), and recompute the seasonally adjusted data. What is the effect of the outlier?

```{r}
p1 = plastics
p1[50] = p1[50] + 500
fit_p1 = decompose(p1, type="multiplicative")
p1_s = seasadj(fit_p1)
plot(p1_s)
```

### F. Does it make any difference if the outlier is near the end rather than in the middle of the time series?

```{r}
p2 = plastics
p2[30] = p2[30] + 500
fit_p2 = decompose(p2, type="multiplicative")
p2_s = seasadj(fit_p2)
plot(p2_s)
```

The outlier in the end seems to be affecting the data more then then outlier in the middle.

### G. Use a random walk with drift to produce forecasts of the seasonally adjusted data.

```{r}
fit <- stl(plastics, t.window=15, s.window="periodic", robust=TRUE)
eeadj <- seasadj(fit)
plot(naive(eeadj),
     main="Naive forecasts of seasonally adjusted data")
```


### H. Reseasonalize the results to give forecasts on the original scale.

```{r}
fcast <- forecast(fit, method="naive")
plot(fcast, ylab="New orders index")
```