---
title: "JElikishvili_Assign4"
author: "Joseph Elikishvili"
date: "March 1, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem Set 1

In this problem, we'll verify using R that SVD and Eigenvalues are related as worked out in the weekly module. Given a 3 × 2 matrix A

```{r}
A = matrix(c(1,2,3,-1, 0, 4),byrow=T,nrow=2,ncol=3)

#Calculate AAt and AtA
X = A %*% t(A)
X
Y = t(A) %*% A
Y

#Compute eigenvalues and eigenvectors of X and Y
eigX = eigen(X)
eigY = eigen(Y)

#compute the left-singular, singular values, and right-singular vectors of A using the svd command

svd_var = svd(A)

#Lets compare Eignevectors of X and left_singular vector
eigX$vectors
svd_var$u

#From the above we can clearly see that Eigenvectors of X are equal to $u of A there is just a different sign or multple of scallar of -1.


eigY$values
eigX$values
svd_var$d*svd_var$d

#And from the above we see thatEigenvalues of X are equal to Eigenvalues of Y and are equal to the squares of singular values from svd of A
```

## Problem Set 2

Using the procedure outlined in section 1 of the weekly handout, write a function to compute the inverse of a well-conditioned full-rank square matrix using co-factors. In order to compute the co-factors, you may use built-in commands to compute the determinant.


```{r}
myinverse <- function(A)  {
  if (nrow(A) != ncol(A)) {
    print ("Enter Square matrix, please!")
  }
  
  C = diag(nrow(A), ncol(A))
  
  for (r in 1:nrow(A)) {
    for (c in 1:ncol(A)) {
      C[r,c] = (-1)^(r+c) * det(A[-r,-c])
    }
  }
   return (t(C)/det(A))
}
```

#### Testing

```{r}
A = matrix(c(1,1,3,2,5,6,7,8,9),byrow=T,nrow=3,ncol=3)

#Should get an Identity matrix
A%*%myinverse(A)

#Comparing builtin function with a custom inverse function
myinverse(A)
solve(A)
```