---
title: "IS605-Assign8"
author: "Joseph Elikishvili"
date: "March 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

## Problem Set 1

Your colleague either commutes by train or by the bus. 20 days of the month,
she takes the train and the remaining 10 days she takes the bus. If she takes the
train, she reaches work on time with a probability of 0.9. If she takes the bus, she
frequently gets stuck in traffic and reaches work on time with a probability of 0.5.
Given that she was on time today, what is the probability that she took the bus to
work today?

```{r}
#P(Bus|ontime) = P(ontime|Bus) * P(bus) / P(ontime|Bus) * P(bus) + P(ontime|!=bus) * P(!=bus)
#P(Bus|ontime) = P(ontime|Bus) * P(bus) / P(ontime|Bus) * P(bus) + P(ontime|Train) * P(Train)

#P(Bus) = 0.333
#P(Train) = 0.666
#P(ontime|Bus) = 0.5
#P(ontime|Train) = 0.9


P_busontime = 0.5*0.333/(0.5*0.333+0.9*0.666)
P_busontime
```

## Problem Set 2
In the Grade Network that we looked at in the notes, what happens to the probability of
Difficulty of Course when you present the evidence that the received recommendation letter
was good? In addition, now present the evidence that both SAT scores were good and
the letter of recommendation was good, What is the probability of the Difficulty of Course
now?

```{r}
library(gRain)
library(gRbase)
d <- cptable(~ difficulty, values=c(0.3, 0.7), levels=c("N", "Y"))
i <- cptable(~ intelligence, values=c(0.8, 0.2), levels=c("L", "H"))
s <- cptable(~ sat|intelligence, values=c(0.9, 0.1, 0.2, 0.8), levels=c("L", "H"))
g <- cptable(~ grade|difficulty:intelligence, values=c(0.6,0.4,0.8,0.2,0.1,0.99,0.1,0.9), levels=c("L", "H"))
l <- cptable(~ letter|grade, values=c(0.9, 0.1, 0.05, 0.95), levels=c("L", "H"))

plist <- compileCPT(list(d, i, s, g, l))

plist
plist$sat

prob1 <- grain(plist)

querygrain(prob1, nodes=c("difficulty","intelligence","sat","grade","letter"), type="marginal")

#Adding good recomendation letter
q1 <- setEvidence(prob1, evidence = list(letter = "H"))
querygrain(q1, nodes=c("difficulty"), type="marginal")

#Adding good recomendation letter and good SAT score.
q2 <- setEvidence(prob1, evidence = list(letter = "H", sat = "H"))
querygrain(q2, nodes=c("difficulty"), type="marginal")

```