---
title: "JElikishvili_assign2"
author: "Joseph Elikishvili"
date: "February 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.1

### Show that ATA != AAT in general. (Proof and demonstration.)


Since we know that AB != BA from the general Matrix properties this suggests that AtA != AAt unless specifically proven.


#### Lets demontrsate it
```{r}
A = matrix(c(1,1,3,2),byrow=T,nrow=2,ncol=2)
AtA = A%*%t(A)
AAt = t(A)%*%A

AtA
AAt
```

#### As we can see from above, AtA != AAt

## 1.2
#### For a special type of square matrix A, we get AT A = AAT. Under what conditions could this be true? (Hint: The Identity matrix I is an example of such a matrix).

```{r}
A = matrix(c(5,1,1,5),byrow=T,nrow=2,ncol=2)
AtA = A%*%t(A)
AAt = t(A)%*%A

AtA
AAt
```

#### The above property holds holds for symetric matricies.

## 2.1

#### Function will print U matrix followed by L
```{r}

LU <- function(A)  {
  L1 = diag(nrow(A))
  L2 = diag(nrow(A))
  L3 = diag(nrow(A))
  L4 = diag(nrow(A))

  #print(A)
  if (nrow(A) == 2) 
  {
    for (r in 2:nrow(A))
    {
      pivot = (A[r,1]/A[1,1])
      A[r,] = A[r,] - pivot*A[1,]
      L1[r,1] = pivot
      L=L1
    }
  }
  
  #print (L)
  
  if (nrow(A) == 3) {
    
    pivot = (A[2,1]/A[1,1])
    A[2,] = A[2,] - pivot*A[1,]
    L1[2,1] = -pivot
    
    pivot = (A[3,1]/A[1,1])
    A[3,] = A[3,] - pivot*A[1,]
    L1[3,1] = -pivot
    L1=solve(L1)
    
    pivot = (A[3,2]/A[2,2])
    A[3,] = A[3,] - pivot*A[2,]
    L2[3,2] = -pivot
    L2=solve(L2)
    L=L1%*%L2
    
  }
  
  if (nrow(A) == 4) 
  {
    pivot = (A[2,1]/A[1,1])
    A[2,] = A[2,] - pivot*A[1,]
    L1[2,1] = -pivot
    
    pivot = (A[3,1]/A[1,1])
    A[3,] = A[3,] - pivot*A[1,]
    L1[3,1] = -pivot
    
    pivot = (A[4,1]/A[1,1])
    A[4,] = A[4,] - pivot*A[1,]
    L1[4,1] = -pivot
    L1=solve(L1)
    
    pivot = (A[3,2]/A[2,2])
    A[3,] = A[3,] - pivot*A[2,]
    L2[3,2] = -pivot
    
    pivot = (A[4,2]/A[2,2])
    A[4,] = A[4,] - pivot*A[2,]
    L2[4,2] = -pivot
    
    L2=solve(L2)
    
    pivot = (A[4,3]/A[3,3])
    A[4,] = A[4,] - pivot*A[3,]
    L3[4,3] = -pivot
    L3=solve(L3)
    
    L=L1%*%L2%*%L3
    
  }

   if (nrow(A) == 5) 
  {
    pivot = (A[2,1]/A[1,1])
    A[2,] = A[2,] - pivot*A[1,]
    L1[2,1] = -pivot
    
    pivot = (A[3,1]/A[1,1])
    A[3,] = A[3,] - pivot*A[1,]
    L1[3,1] = -pivot
    
    pivot = (A[4,1]/A[1,1])
    A[4,] = A[4,] - pivot*A[1,]
    L1[4,1] = -pivot
    
    pivot = (A[5,1]/A[1,1])
    A[5,] = A[5,] - pivot*A[1,]
    L1[5,1] = -pivot
    L1=solve(L1)
    
    
    pivot = (A[3,2]/A[2,2])
    A[3,] = A[3,] - pivot*A[2,]
    L2[3,2] = -pivot
    
    pivot = (A[4,2]/A[2,2])
    A[4,] = A[4,] - pivot*A[2,]
    L2[4,2] = -pivot
    
    pivot = (A[5,2]/A[2,2])
    A[5,] = A[5,] - pivot*A[2,]
    L2[5,2] = -pivot
    L2=solve(L2)
    
    pivot = (A[4,3]/A[3,3])
    A[4,] = A[4,] - pivot*A[3,]
    L3[4,3] = -pivot
    
    pivot = (A[5,3]/A[3,3])
    A[5,] = A[5,] - pivot*A[3,]
    L3[5,3] = -pivot
    L3=solve(L3)
    
    pivot = (A[5,4]/A[4,4])
    A[5,] = A[5,] - pivot*A[4,]
    L4[5,4] = -pivot
    L4=solve(L4)
    
    L=L1%*%L2%*%L3%*%L4
  }

  return (list('upper'=L, 'lower'=A))
}
```
  
Testing 2x2
```{r}
A = matrix(c(1,1,3,2),byrow=T,nrow=2,ncol=2)
l = LU(A)
l
l$upper%*%l$lower
```

Testing 3x3
```{r}
A = matrix(c(1,1,3,2,4,7,6,3,6),byrow=T,nrow=3,ncol=3)
l = LU(A)
l
l$upper%*%l$lower
```

Testing 4x4
```{r}
A = matrix(c(1,1,3,2,4,7,6,3,6,5,1,3,7,2,7,16),byrow=T,nrow=4,ncol=4)
l = LU(A)
l
l$upper%*%l$lower
```

Testing 5x5
```{r}
A = matrix(c(1,1,3,2,4,7,6,3,6,5,1,3,7,2,7,16,1,2,3,4,5,6,7,8,9),byrow=T,nrow=5,ncol=5)

l = LU(A)
l
l$upper%*%l$lower
```