---
title: "606-HW5"
author: "Joseph Elikishvili"
date: "November 13, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 5.6 
Working backwards, Part II. A 90% confidence interval for a population mean is (65,
77). The population distribution is approximately normal and the population standard deviation
is unknown. This confidence interval is based on a simple random sample of 25 observations.
Calculate the sample mean, the margin of error, and the sample standard deviation.

90% CI = (65,77)
n = 25
df=25-1=24
S = ?
Mean = ?
t = qt(.05,24) = 1.71

Mean = 65 + ME
ME = t*SE

ME = (77-65)/2 = 6
Mean = 65 + 6 = 71

SE = ME/t 
SE = 6/1.71 = 3.508

SE = S/SQRT(n) 
S = SE*SQRT(n)
S = 3.508*5 = 17.54

Awnser: Mean = 71, S = 17.54 


## 5.14


5.14 SAT scores. SAT scores of students at an Ivy League college are distributed with a
standard deviation of 250 points. Two statistics students, Raina and Luke, want to estimate the
average SAT score of students at this college as part of a class project. They want their margin of
error to be no more than 25 points.
(a) Raina wants to use a 90% confidence interval. How large a sample should she collect?
(b) Luke wants to use a 99% confidence interval. Without calculating the actual sample size,
determine whether his sample should be larger or smaller than Raina's, and explain your
reasoning.
(c) Calculate the minimum required sample size for Luke.

n = (SD*z/ME)^2

a) SD = 250, z(.05) = 1.31, ME = 25.  n = (250*1.31/25)^2 = 171.61 = 172.
b) n will increase. Mathimatically - Since we are multipling  SD by z and z value will increase, so overall value will increae, Also its just logical tht we need larger sample data to achive more precise estimates.
c) n = (250*2.58/25)^2 = 665.64 = 666.






## 5.20

5.20 High School and Beyond, Part I. The National Center of Education Statistics conducted
a survey of high school seniors, collecting test data on reading, writing, and several other subjects.
Here we examine a simple random sample of 200 students from this survey. Side-by-side box plots
of reading and writing scores as well as a histogram of the di???erences in scores are shown below.

(a) Is there a clear di???erence in the average reading and writing scores?
- Yes, the writing scores have a higher mean the reading scores.

(b) Are the reading and writing scores of each student independent of each other?
- The cores are part of one study and conducted on the same 200 students, so I would say they are dependent on each other.
(c) Create hypotheses appropriate for the following research question: is there an evident di???erence
in the average scores of students in the reading and writing exam?
H0 - There is no difference bewteen reading and writing socres
Ha - There is a difference between the two scores.

(d) Check the conditions required to complete this test.
- n>30
- Normality test would pass

(e) The average observed di???erence in scores is ¯xread???write = ???0.545, and the standard deviation
of the di???erences is 8.887 points. Do these data provide convincing evidence of a di???erence between the average scores on the two exams?

se=SDdiff/SQRT(ndiff) = 8.8887/sqrt(200) = 0.6285
t = 0+0.545/0.6258 = 0.87
df=200-1=199
pt(0.87, df=199) = 0.8073257
p value is > 0.05, so we fail to reject H0 and conclude that there is not enough proof to think there is a difference.

(f) What type of error might we have made? Explain what the error means in the context of the
application.

- If we made an error, that means we rejected the H0, so its a Type II error, which means we claimed there is a difference, while there isn't

(g) Based on the results of this hypothesis test, would you expect a confidence interval for the
average di???erence between the reading and writing scores to include 0? Explain your reasoning.

- Yes I would expect a 0 to be within the range. IF we take 1SD range of the mean difference we will include a 0, in fact we don;t even need a 1SD as -0.545 is pretty close to the 0.

## 5.32

Each year the US Environmental Protection Agency (EPA) releases fuel economy data on cars manufactured in that year.
Below are summary statistics on fuel efficiency (in miles/gallon) from random samples of cars with
manual and automatic transmissions manufactured in 2012. Do these data provide strong evidence
of a di???erence between the average fuel efficiency of cars with manual and automatic transmissions
in terms of their average city mileage? Assume that conditions for inference are satisfied.

#### H0 - there is no difference

#### Ha - there is a difference

```{r}
n=26
m1=16.2
sd1=3.58
m2=19.85
sd2=4.51

mean=m1-m2
se=sqrt(((sd1^2)/26)+((sd2^2)/26))
t=(mean-0)/se
pt(t, df=25)
```

based on the fact that p<0.05, we reject the null hypotheses and conclude that there is a difference in fuel effisiencey between cars with manual and automatic transmitions.


## 5.48 

Work hours and education. The General Social Survey collects data on demographics,
education, and work, among many other characteristics of US residents.47 Using ANOVA, we can
consider educational attainment levels for all 1,172 respondents at once. Below are the distributions
of hours worked by educational attainment and relevant summary statistics that will be helpful in
carrying out this analysis.


(a) Write hypotheses for evaluating whether the average number of hours worked varies across the
five groups.


#### H0 - the means are not different
#### Ha - at least one of the means is different from others

(b) Check conditions and describe any assumptions you must make to proceed with the test.
1. Independence - the data seems to be independent
2. Approximately normal - the data seems to be approximately normally distributed
3. Constant Variance - data seems to have variability approximately with the same range

(c) Below is part of the output associated with this test. Fill in the empty cells.

```{r}
DFe = 1172-5
DFg = 5-1

n=c(121,546,97,253,155) 
SD=c(15.81,14.97,18.1,13.62,15.51)
MEAN=c(38.67,39.6,41.39,42.55,40.85)

SSG = sum(n*(MEAN-40.45)^2)
MSG = (1/DFg)*SSG
SSE=267382
MSE=SSE/DFe
MSE

f = MSG/MSE
f
```

degree = 1167
residual = 4
total_df = 1167+4=1171
SSG=2004.1
total_SS = 2004.1+267382=269386.1
MSE=229.12
f=2.187

(d) What is the conclusion of the test?

p=0.0682>0.05, therefore we do not have enough evidence to reject H0 and do not have enough evidence to suggest that the means are different.
