---
title: "606-HW6"
author: "Joseph Elikishvili"
date: "November 15, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 6.6 

2010 Healthcare Law. On June 28, 2012 the U.S. Supreme Court upheld the much debated 2010 healthcare law, declaring it constitutional. A Gallup poll released the day after this decision indicates that 46% of 1,012 Americans agree with this decision. At a 95% confidence level, this
sample has a 3% margin of error. Based on this information, determine if the following statements are true or false, and explain your reasoning.

(a) We are 95% confident that between 43% and 49% of Americans in this sample support the decision of the U.S. Supreme Court on the 2010 healthcare law.

#### Incorrect. We are 100% confident that 46% of Americans in this sample support the decision of the U.S. Supreme Court.  Since the statement talks about the sample, we have all the data we need and no confidence interval is needed.

(b) We are 95% confident that between 43% and 49% of Americans support the decision of the U.S. Supreme Court on the 2010 healthcare law.

#### Correct. We are estimating proportion of entire population using the sample we have.

(c) If we considered many random samples of 1,012 Americans, and we calculated the sample proportions of those who support the decision of the U.S. Supreme Court, 95% of those sample proportions will be between 43% and 49%.

#### Correct. 95% of those samples will show similar results and 5% will be outside of CI.

(d) The margin of error at a 90% confidence level would be higher than 3%.

#### Incorrect. lower confidence level =  more precise result, so margin of error should decrese. 

```{r}
```

## 6.12 

Legalization of marijuana, Part I. The 2010 General Social Survey asked 1,259 US residents: "Do you think the use of marijuana should be made legal, or not?" 48% of the respondents said it should be made legal.

(a) Is 48% a sample statistic or a population parameter? Explain.

#### It is a sample statistic. We are not making any assumptions about population, if we did we would have some sort of confidence level and margin of error along with it.

(b) Construct a 95% confidence interval for the proportion of US residents who think marijuana should be made legal, and interpret it in the context of the data.

```{r}
p=0.48
me = 1.96*sqrt((0.48*0.52)/1259)
c(p-me,p+me)
```

#### We are 95% confident that 45.2%-50.8% of US residents think that marijuana should be legal.

(c) A critic points out that this 95% confidence interval is only accurate if the statistic follows a normal distribution, or if the normal model is a good approximation. Is this true for these data? Explain.

#### We have a pretty high n>1000 which should solve the issue if data was not normaly distributed, besides the data should be normally distributed in this case.

(d) A news piece on this survey's findings states, "Majority of Americans think marijuana should be legalized." Based on your confidence interval, is this news piece's statement justified?

#### Not really. It would be a stretch. 50.1% does fall within the confidence interval, but the interval is clearly pointing to be less then 50% for the most part, besides, having CI so close to 50% it would be misleading to state the above. Saying that we are 95% confident that 45.2%-50.8% of Population supports it would be a better choice and is pretty self explanatory.

```{r}
```

## 6.20

Legalize Marijuana, Part II. As discussed in Exercise 6.12, the 2010 General Social Survey reported a sample where about 48% of US residents thought marijuana should be made legal. If we wanted to limit the margin of error of a 95% confidence interval to 2%, about how many Americans would we need to survey ?

```{r}
n=1.96^2*(0.48*0.52)/0.02^2
n
```

#### n = 2398


## 6.28 

Sleep deprivation, CA vs. OR, Part I. According to a report on sleep deprivation by the Centers for Disease Control and Prevention, the proportion of California residents who reported insufficient rest or sleep during each of the preceding 30 days is 8.0%, while this proportion is 8.8% for Oregon residents. These data are based on simple random samples of 11,545 California and 4,691 Oregon residents. Calculate a 95% confidence interval for the di???erence between the proportions of Californians and Oregonians who are sleep deprived and interpret it in context of the data.

```{r}
p1=0.08
p2=0.088
p=p1-p2
me=1.96*sqrt((p1*(1-p1))/11545+(p2*(1-p2))/4691)
c(p-me,p+me)
```

#### Since 0 is part of the interval, we cannot reject the null hypotheses and conclude that there is not enough evidence that there is a difference in proportions of sleep deprevation in CA and Oregon. 


## 6.44 

Barking deer. Microhabitat factors associated with forage and bed sites of barking deer in Hainan Island, China were examined from 2001 to 2002. In this region woods make up 4.8% of the land, cultivated grass plot makes up 14.7% and deciduous forests makes up 39.6%. Of the 426 sites where the deer forage, 4 were categorized as woods, 16 as cultivated grassplot, and 61 as deciduous forests. The table below summarizes these data.

(a) Write the hypotheses for testing if barking deer prefer to foragein certain habitats over others.

#### H0 proportion of deer forage is in accordance with the provided data
#### Ha proportion of deer forage is not in accordance with the provided data


(b) What type of test can we use to answer this research question?

#### We can use a goodness of fit - Chi-square test

(c) Check if the assumptions and conditions required for this test are satisfied.

#### Random sampling - we have no evidence that shows this was not random
#### At least 5 cases - We have more cases that were combined into 4.

(d) Do these data provide convincing evidence that barking deer prefer to forage in certain habitats over others? Conduct an appropriate hypothesis test to answer this research question.

```{r}
x=c(426*0.048, 426*0.147, 426*.396, 426*(1-0.048-0.147-0.396))
z=c((4-x[1])/sqrt(x[1]),(16-x[2])/sqrt(x[2]),(67-x[3])/sqrt(x[3]),(345-x[4])/sqrt(x[4]))
chi=z[1]^2+z[2]^2+z[3]^2+z[4]^2
chi
1-pchisq(chi,3)
```

#### we have p<0.05 so we reject the H0 and conclude that proportion of deer forage is not in accordance with the provided data and therefore conclude that barking deer prefer to forage in certain habitats over others.

## 6.48 

Coffee and Depression. Researchers conducted a study investigating the relationship between ca???einated co???ee consumption and risk of depression in women. They collected data on 50,739 women free of depression symptoms at the start of the study in the year 1996, and these women were followed through 2006. The researchers used questionnaires to collect data on ca???einated co???ee consumption, asked each individual about physician-diagnosed depression, and also asked about the use of antidepressants. The table below shows the distribution of incidences
of depression by amount of ca???einated co???ee consumption.

(a) What type of test is appropriate for evaluating if there is an association between co???ee intake and depression?

#### The chi-square test for two-way tables

(b) Write the hypotheses for the test you identified in part (a)

H0 - coffee consumption is not related to depression
Ha - coffee consumption is related to depression

(c) Calculate the overall proportion of women who do and do not su???er from depression.

#### 2,607/50,739 = 0.0514  
#### 5.14% are suffereing from depression, 94.86% are free from depression.

(d) Identify the expected count for the highlighted cell, and calculate the contribution of this cell to the test statistic, i.e. (Observed ??? Expected)2/Expected.

```{r}
expected = 6617*0.0514
expected
(373-expected)^2/expected
```

(e) The test statistic is chi = 20.93. What is the p-value?

```{r}
df=(5-1)*(2-1)
1-pchisq(20.93,df)
```

(f) What is the conclusion of the hypothesis test?

#### p<0.05, so we reject H0 and conclude that there is a connection between coffee and depression.

(g) One of the authors of this study was quoted on the NYTimes as saying it was "too early to
recommend that women load up on extra co???ee" based on just this study.64 Do you agree with
this statement? Explain your reasoning.

#### I would agree with the statement.  Its a pretty significant statement to be made and one study is not enough to issue recomendations to public, besiudes there could be other factors at play as simple as weather change or some recent news of terror attack or election upset or overall economy depression that could shift overtall population to feel more or less anxious and depressed, so this is indication should not be ignored, but rather studied in more detail.  Maybe additional similar tests over the period of some time showing the same results would be a stronger indicator if there is truth to the study.
