---
title: "MSDA Data 607 Assignment #1"
author: "Joseph Elikishvili"
date: "September 11, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RMySQL)
library(RSQLite)
library(ggplot2)
```

## Introduction

The purpose of this asignment is to create a database containing rankings of 6 recent movies by 5 different users, connect to the database from R and load the database into a dataframe. This particular implementation is using Mysql as a database server and is using RMySQL package to istablish the connection to database and retrieve the data. 


```{r cars}
```

##### below is the copy of sql script which is used to create and populate the database

```{r, echo=TRUE}

# DROP DATABASE IF EXISTS moviedb;
# CREATE database moviedb;
# use moviedb;
# 
# CREATE TABLE users (
# userID int not null auto_increment,
# fname varchar(20),
# lname varchar(20),
# primary key (userID)
# );
# 
# INSERT INTO users (fname, lname) VALUES
# ('Natalia','Lesechko'),
# ('Victoria','Elikishvili'),
# ('Sergey','Vayner'),
# ('Bing','Bong'),
# ('Dmitry','Yuster');
# 
# CREATE TABLE movies (
# movieID int not null auto_increment,
# title varchar (30),
# genre varchar(20),
# imdbrating float,
# primary key (movieID)
# );
# 
# INSERT INTO movies (title, genre, imdbrating) VALUES
# ('Jason Bourne','Action',6.9),
# ('War Dogs','Comedy',7.3),
# ('Suicide Squad','Action',6.7),
# ('Inside Out','Animation',8.3),
# ('Zootopia','Animation',8.1),
# ('Now you see me 2','Action',6.6);
# 
# CREATE TABLE reviews(
# userID int,
# movieID int,
# userrating int
# );
# 
# INSERT INTO reviews (userID, movieID, userrating) VALUES
# (1,1,4),(1,2,3),(1,3,2),(1,4,4),(1,5,4),(1,6,4),
# (2,1,2),(2,2,2),(2,3,1),(2,4,5),(2,5,5),(2,6,3),
# (3,1,5),(3,2,5),(3,3,3),(3,4,4),(3,5,3),(3,6,3),
# (4,1,4),(4,2,3),(4,3,4),(4,4,5),(4,5,5),(4,6,3),
# (5,1,5),(5,2,5),(5,3,3),(5,4,4),(5,5,4),(5,6,3);
# 
# SELECT users.fname, users.lname, movies.title, movies.genre, movies.imdbrating, reviews.userrating from reviews
# JOIN users on users.userID = reviews.userID
# JOIN movies on reviews.movieID = movies.movieID
# ORDER BY title;
```


##### Next we initiate a conection with the local database, create the sql string and run the query and store the result in a dataframe and finally display the results. 


```{r}
rmysql.settingsfile<-"C:/ProgramData/MySQL/MySQL Server 5.7/my.ini"
con <- dbConnect(RMySQL::MySQL(), default.file=rmysql.settingsfile, dbname = "moviedb", username=NULL, password=NULL)
sql <- "SELECT users.fname, users.lname, movies.title, movies.genre, movies.imdbrating, reviews.userrating from reviews JOIN users on users.userID = reviews.userID JOIN movies on reviews.movieID = movies.movieID ORDER BY title;"
res <- dbGetQuery(con, sql)
res
```

#####  Next we aggrigate the rankings to calculate the mean ranking for each of the movies and compare it with IMDB ranking and check the correlation between the two. 
```{r}
a=aggregate(res[, 6], list(res$title, res$imdbrating), mean)
 colnames(a) <- c("Move_Title", "User_Ranking","IMDB_Ranking")
a
```

##### Below we are plotting the user ranking and IMDB ranking by movie
```{r}
ggplot(a, aes(x=Move_Title, y=User_Ranking)) + geom_bar(stat="identity")
ggplot(a, aes(x=Move_Title, y=IMDB_Ranking)) + geom_bar(stat="identity")
```

##### Finally we check for correlation between the two rankings
```{r}
cor(a$User_Ranking,a$IMDB_Ranking)
```

##### The second part of the project was not designed to provide any kind of conclusion, I was simply interested to see how it relates to IMDB rankings, nevertheless correlation of .81 is interesting considering we only had limited data.